### 2014-08-22 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Additional edits to ventilation timeline and details

\begin{table}[!ht]
\caption[Timeline of ventilation events in the simulation]{Timeline of ventilation events in the simulation}
\begin{tabular}{ccll}
\toprule
FDS Simulation Time  &  Ventilation Area  &  Ventilation Type    &  Ventilation Location     \\
{(s)}                &  (m$^2$)           &                      &                           \\
\midrule
0                    &  1.47              &  Door                &  Front Exterior           \\
0                    &  10.1              &  Overhead Door       &  Front Exterior (Garage)  \\
0                    &  1.68              &  Door                &  Interior (Stairwell)     \\
0                    &  1.68              &  Door                &  Interior (Garage)        \\
342                  &  1.89              &  Sliding Glass Door  &  Rear Basement Exterior   \\
383                  &  1.89              &  Sliding Glass Door  &  Rear Basement Exterior   \\
383                  &  1.68              &  Door                &  Left Basement Exterior   \\
418                  &  2.52              &  Window              &  Rear Basement Exterior   \\
440                  &  2.31              &  Window              &  Rear Basement Exterior   \\
450                  &  3.78              &  Sliding Glass Door  &  Rear Basement Exterior   \\
\bottomrule
\end{tabular}
\label{tab:ventilation_timeline}
\end{table}

>>>>

\begin{table}[!ht]
\caption[Timeline of ventilation events in the simulation]{Timeline of ventilation events in the simulation}
\begin{tabular}{ccll}
\toprule
Simulation Time      &  Ventilation Area  &  Ventilation Type    &  Ventilation Location     \\
{(s)}                &  (m$^2$)           &                      &                           \\
\midrule
0                    &  1.47              &  Door                &  Front Entry Exterior     \\
0                    &  10.1              &  Overhead Door       &  Front Garage Exterior    \\
0                    &  1.68              &  Door                &  Stairwell Interior       \\
0                    &  1.68              &  Door                &  Garage Interior          \\
342                  &  1.89              &  Sliding Glass Door  &  Rear Basement Exterior   \\
383                  &  1.89              &  Sliding Glass Door  &  Rear Basement Exterior   \\
383                  &  1.68              &  Door                &  Left Basement Exterior   \\
418                  &  2.52              &  Window              &  Rear Basement Exterior   \\
440                  &  2.31              &  Window              &  Rear Basement Exterior   \\
450                  &  3.78              &  Sliding Glass Door  &  Rear Basement Exterior   \\
\bottomrule
\end{tabular}
\label{tab:ventilation_timeline}
\end{table}
